Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-16 papers/B1555_EdgeOn/B1555_letter.tex
Added initial version of figures

\shorttitle{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
\shortauthors{TBD}

@@

@@

The B1555+375 system was observed using the NIRC2 camera on the Keck 2
Telescope on the night of 2012 May 16 UT.  The adaptive optics system
was used, with the corrections derived from the laser guide star and a
$R$=14.4 tip-tilt that was located 45$^{\prime\prime}$ from the lens
system.  The ``narrow camera'' mode was used, giving a field of view
of roughly 10$^{\prime\prime}$\ on a side and a pixel scale of 10~mas.
Six dithered 300~s exposures were obtained in $K^{\prime}$ band.  The
data were reduced with the standard SHARP pipeline, which is a
python-based package that is a refinement of the process described in
\citet{Auger_EELS1}.  A ??x?? cutout of the final reduced image
is shown in Fig.~??b and again in Fig.~??c with contours from the
MERLIN radio observations of \citet{Marlow} overlaid.  There are several
notable features in the Keck AO data.  These
include the nearly complete lack of emission associated with the
B and D lensed images, as can be seen by comparing the radio contours
to the $K^\prime$-band emission, and faint but clearly visible emission
from what appears to be an edge-on lensing galaxy.

@@

The B1555+375 system was also observed by the Hubble Space Telescope
(HST) in three broad bands.  The optical data were obtained with the
Wide-Field Planetary Camera 2 (WFPC2) in the $F555W$ and $F814W$ bands
(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
Spectrograph (NICMOS) was used to observe the system in the $F160W$
band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
obtained with the NIC2 camera.  We reduced all of the archival HST
data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
MATT], producing final drizzled images with pixel scales of
50~mas.  The reduced images are shown in Figure~??.  The lens system
is not detected at high significance in the optical bands, but is
clearly seen in the NICMOS $F160W$ image.  The edge-on lensing galaxy 
stands out in the NICMOS image.

>>>>

\shorttitle{Beware the Effect of Edge-on Disks}
\shortauthors{Hsueh et al.}

@@

\begin{figure*}
\plotone{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.
%
\label{fig:multiband}}
\end{figure*}

@@

The B1555+375 system was observed using the NIRC2 camera on the Keck 2
Telescope on the night of 2012 May 16 UT.  The adaptive optics system
was used, with the corrections derived from the laser guide star and a
$R$=14.4 tip-tilt that was located 45$^{\prime\prime}$ from the lens
system.  The ``narrow camera'' mode was used, giving a field of view
of roughly 10$^{\prime\prime}$\ on a side and a pixel scale of 10~mas.
Six dithered 300~s exposures were obtained in $K^{\prime}$ band.  The
data were reduced with the standard SHARP pipeline, which is a
python-based package that is a refinement of the process described in
\citet{Auger_EELS1}.  A cutout of the final reduced image is shown in
Fig.~\ref{fig:multiband} and again in Fig.~\ref{fig:merlin} with
contours from the MERLIN radio observations of \citet{Marlow}
overlaid.  There are several notable features in the Keck AO data.
These include the nearly complete lack of emission associated with the
B and D lensed images, as can be seen by comparing the radio contours
to the $K^\prime$-band emission, and faint but clearly visible
emission from what appears to be an edge-on lensing galaxy.

\begin{figure}
\plotone{1555_ao_merlin_overlay.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.
%
\label{fig:merlin}}
\end{figure}

@@

The B1555+375 system was also observed by the Hubble Space Telescope
(HST) in three broad bands.  The optical data were obtained with the
Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
Spectrograph (NICMOS) was used to observe the system in the $F160W$
band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
obtained with the NIC2 camera.  We reduced all of the archival HST
data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
MATT], producing final drizzled images with pixel scales of
50~mas.  The reduced images are shown in Figure~??.  The lens system
is not detected at high significance in the optical bands, but is
clearly seen in the NICMOS $F160W$ image.  The edge-on lensing galaxy 
stands out in the NICMOS image.
